---
title: "Week 13 pdf"
author: "Khue Tran"
date: "4/21/2020"
output: pdf_document
---

---
title: "Week 13"
output: html_notebook
---


# Libraries
```{r, message = F}
library(tidyverse)
library(twitteR)
library(tm)
library(SnowballC)
library(textstem)
library(wordcloud)
library(ldatuning)
library(topicmodels)
library(tidytext)
library(caret)
library(LiblineaR)
```


# Data Import and Cleaning
```{r}
api
apiSecret 
access 
accessSecret 
setup_twitter_oauth(api, apiSecret,access,accessSecret)
```


```{r}
imported <- searchTwitter("#baking", 5000)
imported_tbl <- twListToDF(imported) %>%
  dplyr::filter(isRetweet == F)
imported_tbl$text <- imported_tbl$text %>% 
  iconv("UTF-8", "ASCII", sub="")
```



```{r}
# preprocessed lemmas
twitter_cp <- VCorpus(VectorSource(imported_tbl))

stops <- c(stopwords(kind = 'en'), '#baking', 'baking', 'false', 'true')
twitter_cp <- tm_map(twitter_cp, PlainTextDocument)
twitter_cp <- tm_map(twitter_cp, content_transformer(str_to_lower))
twitter_cp <- tm_map(twitter_cp, removeWords, stops)
twitter_cp <- tm_map(twitter_cp, removeNumbers)
twitter_cp <- tm_map(twitter_cp, removePunctuation)
twitter_cp <- tm_map(twitter_cp, stripWhitespace)
twitter_cp <- twitter_cp[-grep("^[http]", twitter_cp[[1]]$content)]
twitter_cp <- twitter_cp[-grep("^[href]", twitter_cp[[1]]$content)]



# unigram and bigram DTM
# RWeka package does not run
# myTokenizer <- function(x) {NGramTokenizer(x,
#                                            Weka_control(min=1, max=2))}
# twitter_dtm <- DocumentTermMatrix(twitter_cp,
#                                   control = list(
#                                     tokenize = myTokenizer))


twitter_dtm <- DocumentTermMatrix(twitter_cp)

# eliminate sparse terms
twitter_slimmed <- removeSparseTerms(twitter_dtm, .95)

tokenCounts <- apply(twitter_slimmed, 1, sum)
twitter_cleaned_dtm <- twitter_slimmed[tokenCounts > 0,]
twitter_tbl <- as.tibble(as.matrix(twitter_cleaned_dtm))

# delete cases for tweets where no tokens were retained
dropped_tbl <- imported_tbl %>%
  unnest_tokens(token, text, token = "ngrams", n = 1) %>%
  filter(token %in% names(twitter_tbl)) %>%
  arrange(token)
```



# Visualization
```{r}
# wordcloud
wordCounts <- colSums(twitter_tbl)
wordNames <- names(twitter_tbl)
wordcloud(wordNames, wordCounts, max.words = 50)

# bar chart
tibble(wordNames, wordCounts) %>%
  arrange(desc(wordCounts)) %>%
  top_n(20) %>%
  mutate(wordNames = reorder(wordNames, wordCounts)) %>%
  ggplot(aes(x = wordNames, y = wordCounts)) + geom_col() + coord_flip() + theme_classic()
```


# Analysis

## Topic Modeling
```{r}
tuning <- FindTopicsNumber(twitter_cleaned_dtm,
                           topics = seq(2,15,1), 
                           metrics = c("Griffiths2004", "CaoJuan2009","Arun2010", "Deveaud2014"),
                           verbose = T)
FindTopicsNumber_plot(tuning)
lda_results <- LDA(twitter_cleaned_dtm, 4) # num topics based on plot
lda_betas <- tidy(lda_results, matrix="beta")
lda_gammas <- tidy(lda_results, matrix="gamma")

(topic_top <- lda_betas %>% 
  group_by(topic) %>%
  top_n(10, beta) %>%
  arrange(topic, -beta))
```


Topics 1, 2, and 3 are similar, with Topic 2 related more to actions related to baking and Topic 1 and 3 related more to baking recipes and ingredients. Topics 4 seems to include hashtags related to baking.

## Machine Learning
```{r}
dropped <- dropped_tbl %>%
  group_by(token) %>%
  summarise(popularity = sum(favoriteCount))

transpose_df <- function(df) {
  t_df <- data.table::transpose(df)
  colnames(t_df) <- rownames(df)
  rownames(t_df) <- colnames(df)
  t_df <- t_df %>%
    tibble::rownames_to_column(.data = .) %>%
    tibble::as_tibble(.)
  return(t_df)
}

twitter_tbl_ml <- transpose_df(twitter_tbl) %>%
  inner_join(dropped, by = c("rowname" = "token")) %>%
  inner_join(lda_betas, by = c("rowname" = "term")) %>%
  rename(token = rowname) %>%
  mutate(topic = factor(topic))
```


```{r}
svm_mod1 <- train(popularity ~ token,
                 data = twitter_tbl_ml,
                 # SVM
                 method = "svmLinear3", 
                 # missing values
                 # na.action = na.pass,
                 # Set cross-validation to be 10 fold
                 trControl = trainControl("cv", number = 10)) 


svm_mod2 <- train(popularity ~ token + topic,
                 data = twitter_tbl_ml,
                 # SVM
                 method = "svmLinear3", 
                 # Set cross-validation to be 10 fold
                 trControl = trainControl("cv", number = 10)) 

# comparing cross-validated
summary(resamples(list(svm_mod1, svm_mod2)))
dotplot(resamples(list(svm_mod1, svm_mod2)), metric="RMSE")
```


## Final Interpretation


Based on the comparison of the two models and the topics extracted from the analysis, it seems like topics are not very meaningful and too noisy, leading to the model 2 with topic as the added predictors are not 

